### 2022-04-18 paper/ase22/intro.tex
intro

Software testing is the crucial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, NLP application is a
branch of artifical intelligence software, and testing NLP application
also becomes important process as well.

>>>>

Software testing is the essential component of software development
process.  It evaluates an attribute or capability of the software and
determines quality of the software by examining the behavior of the
software.  Software testing in the early stage of the development
finds bugs, and fixing them saves amount of costs. \Ml (ML) application is a
primary branch of artifical intelligence software, and testing the application
also becomes important process for NLP model.

In addition, reliable software testing methodology ensures software
quality to end users in that the software meets requirements by
verification and validation.

Regarding that,
